Gap formation and stability in non-isothermal self-gravitating discs

### 2014-06-23 paper/results.tex
brief notes on what information should be included

%we checked that open bc doesn't affect gap structure
%checked that t=200 plots are similar to t=100

@@

\section{Gaps in massive discs (MKL)}
%% We first examine disc models with $Q_o=1.5$. We set the physical
%% viscosity $\hat{\nu}=10^{-9}$, so that the only energy source is
%% through shock-heating (via artificial viscosity) and the $\mathcal{C}$
%% function when $e\Sigma<e_i\Sigma_i$. The numerical resolution is
%% $N_r\times N_\phi = 512\times 1024$.

>>>>

\subsection{Gap structure}
{\bf plots of the gap structure before instability sets in, e.g. at
  t=30. surface density perturbation, gen. vortensity perturbation,
  aspect-ratio. compare diff. beta
}

\subsection{Linear stability}
{\bf present `planet-off' simulations. compare growthrate and dominant
  m as function of beta. although focus is linear stability
  properties, can also show non-linear evolution for completeness (to
  be compared with planet-on sims. later)
}

\subsection{Non-linear evolution}
           {\bf describe a few planet-on sims. as func. of beta. lifetime. 
           }
%we checked that open bc doesn't affect gap structure
%checked that t=200 plots are similar to t=100

@@

%%\section{Gaps in massive discs (MKL)}
%% We first examine disc models with $Q_o=1.5$. We set the physical
%% viscosity $\hat{\nu}=10^{-9}$, so that the only energy source is
%% through shock-heating (via artificial viscosity) and the $\mathcal{C}$
%% function when $e\Sigma<e_i\Sigma_i$. The numerical resolution is
%% $N_r\times N_\phi = 512\times 1024$.
